\SW: II. New Gravitational Lens Candidates from the CFHTLS Discovered through Citizen Science

### 2015-07-23 doc/sw-cfhtls.tex
AV's and my final edits
closes #217

% AV IS HERE!

\begin{abstract}
We report the discovery of 29 promising (and 59 total) new lens
candidates from the CFHT Legacy Survey (\cfhtls) based on about 11
million classifications performed by citizen scientists as part of the
first \sw lens search.  The goal of the blind lens search was to
identify lens candidates missed by robots (the \rf on galaxy scales and
\af on group/cluster scales) which had been previously used to mine the
\cfhtls for lenses.  We compare some properties of the samples detected
by these algorithms to the \sw sample and find them to be broadly
similar.  The image separation distribution calculated from the \sw
sample shows that previous constraints on the average density profile of
lens galaxies are robust. \sw recovers about 65\% of known lenses, while
the new candidates show a richer variety compared to those found by the
two robots. This detection rate could be increased to 80\% by only using
classifications performed by expert volunteers (albeit at the cost of a
higher false positive rate), indicating that the training and
performance calibration of the citizen scientists is very important for
the success of \sw. In this work we present the SIMCT pipeline, used for
generating {\it in situ} a sample of realistic  simulated lensed images.
This training sample, along with the false positives identified during
the search, has a legacy value for testing future lens finding
algorithms. We make the pipeline and the training set publicly
available.
\end{abstract}

@@

\section{Training sample: Simulated lenses}
\label{sec:ts}

The simulated lenses are important to train citizen scientists who may be
new to the task of finding lenses, but they are also crucial for
analysing the classifications performed by the citizen scientists (more
details can be found in \PaperOne, but see \Sref{sec:swap} below for a brief
summary). In this section, we describe the framework used for generating the
simulated lens sample and give details of the sample itself along with
some of its known limitations.

@@

\subsection{Methodology}
\label{sec:simmethod}

@@

We also add external shear at the centre of the lensing galaxy
drawn randomly from a set range (see \Tref{tab:thresh}. The shear is
expected to affect the lens cross-section for a small number of cases
when the shear strength is high in addition to high lens ellipticity or
the PA of the shear is almost orthogonal to that of the lens
ellipticity. However, the effect of shear on the lens cross-section is
expected to be small for most of the cases and is ignored in the current
implementation of SIMCT.

@@

Once all the parameters are determined for the lens and source models, we once
again use \gravlens to generate simulated lensed images.  After accounting for the shot
noise in the lensed images and convolving them with the seeing in each of
the filters, the simulated image is added to the real \cfhtls~image centred
on the lensing galaxy. Note that we ensure that the lensed galaxies and
lensed quasars do not have the same lensing galaxy in the foreground. Similarly,
the lensing galaxies from the galaxy-scale lenses are distinct from the central
galaxies of group-scale lenses which are described in the following section.

\begin{figure}
\begin{center}
\includegraphics[scale=1.2]{distrib_remu.pdf}
\caption{ \label{fig:remudist}
Einstein radius distribution for all types of lenses. The solid (blue)
curves show the theoretical prediction assuming an SIS model at galaxy-scales
and a total (NFW+Hernquist) model at group scales taken from \citep{More2012}.
}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=1.3]{lensprop.pdf}
\caption{ \label{fig:lensprop}
Distributions of properties of the lensing galaxies of the simulated
sample compared to the known lens sample SARCS.
}
\end{center}
\end{figure*}

@@

Next, we consider the redshift, magnitude and ellipticity distributions
of the lensing galaxies as shown in \Fref{fig:lensprop}. For reference,
we also show SARCS lenses from \citet{More2012}, with arbitrary
normalizations. We find that the properties of the foreground lenses in
the simulated and the real lens samples are broadly similar.

We produce catalogs with lens and source properties for each of the
three types of lenses.  The catalogs typically have lens position,
redshift, magnitudes, Einstein radius, ellipticity (whenever available)
and shear (for galaxy-scale lenses only). For the background sources, we
provide the offset from the lens centre, redshift, magnitudes, total
magnification, number of lensed images. Additionally, when possible,
ellipticity and effective radius of the background galaxies have also
been provided. These catalogs are available from
\texttt{https://github.com/anupreeta27/SIMCT} and the
simulated lens image sample is available from the authors on request.

@@

The parameters required by the models' various scaling relations
primarily depend on the photometry of the galaxies, groups and quasars
detected in the survey. For galaxy-scale lenses, the fainter or higher redshift
lensing galaxies tend to have poor photometric redshift
measurements. Consequently these galaxies were occasionally assigned the wrong
luminosity and velocity dispersion estimates, resulting in
simulated lenses which look implausible or unrealistic.  For example,
the lensed images for some of the failed simulations have larger image
separation than what one would expect from the luminosity and/or size of the
galaxy. We roughly expect mass to follow light, so more massive galaxies
typically look brighter and/or bigger.

@@

\section{Training sample: Duds and Impostors}
\label{sec:dfp}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.6]{cand_fp_P_frac.pdf}
\caption{ \label{fig:stackP}
Distribution of different types of candidates as a function of the
posterior probability $P$. The types of the candidates are the false
positives (FPs), the new candidates and the known candidates. The new
and known candidates have higher detection rate for higher values of $P$,
as expected.}
\end{center}
\end{figure}

@@

Each subject (image cutout) is assigned a prior probability of
$2\times10^{-4}$ of containing a lens system. Every volunteer
is assigned an agent characterised by a $2\times2$ confusion matrix~$\CM$,
which quantifies the volunteer's ability to correctly classify an image
as containing a lens ($\PL = P_L$) or not containing a lens ($\PD = P_D$).
The values of
these confusion matrix elements are determined based on the performance of the
volunteer on the training sample, specifically, $P_L$ (and $P_D$) is
determined based on the fraction of simulated lenses (and, respectively, duds)
correctly classified. After every classification, the agent updates the
probability of the classified subject based on the volunteer's classification
and the confusion matrix, according to Bayes' theorem.
The agent's confusion matrix is updated after the
classification of every training image. The thresholds for the
probabilities to accept or reject a subject if it contains a lens or does
not contain one can be chosen in SWAP. Those images which cross
these threshold values are ``retired'', and are not subsequently shown to the
volunteers. In this way, the crowd can use its time efficiently in
inspecting previously unclassified subjects.

SWAP was run nightly during \StageOne in order to retire subjects and inject new
ones in to the classification stream. The subjects that passed the detection
threshold at the end of \StageOne were served again at \StageTwo for careful
re-inspection. Each subject, after \StageTwo, has a posterior
probability $P$. In the ideal case, all images containing lenses will have high $P$
values and those without lenses will have low $P$ values. In practice, we expect a
small fraction of the real lenses (or non-lenses) to be assigned low (or high) $P$
values, thereby decreasing the completeness (or purity) of the final lens
sample. As this is the first lens search with \sw, we want to find a
threshold $P$ value which will result in acceptable levels of completeness and
purity of the final sample of lens candidates.

To achieve this, we selected a total of 665 subjects with $P>0.3$
which were then visually inspected by three of us (as ``lens experts'',
 AM, AV, PJM).  Each images was assigned a grade on a scale of 0 to 3,
representing those images
0) unlikely to contain a lens, 1) possibly containing a lens, 2) probably
containing a lens and 3) almost certainly containing a
lens. The final sample of \sw-\cfhtls lens candidates was
then produced by selecting candidates above a threshold on the
averaged grade~$G$, as described in the next section.

@@

The new \sw lens sample presented here illustrates some of
the advantages of having
citizen scientists find lenses through visual inspection. An algorithm,
by definition will find objects that adhere to a selection criteria that
uses either geometry or flux information from an image. On the other
hand, citizen scientists can interpolate over or
extrapolate beyond the basic selection criteria provided to them.  For
example, the lower blue arc in SW7 is split by a small red galaxy.  An
algorithm typically fails to detect such arcs because the arc is broken
into smaller arclets which then falls below the minimum length or area
allowed for an arc to be detected. Human inspectors have no
problem in interpolating over the broken blue arc over the red galaxy,
understanding that it is a single long arc. The system SW20 has
point-like lensed images which cannot be detected by arc finding
algorithm, whereas the ring finding algorithm may have missed this because of
the atypical colour and structure of the galaxy. Detection of red arcs, for
example, as seen in the SW39 candidate, shows how the volunteers
extrapolate on the colour parameter: the training sample contains
predominantly blue arcs, because the source colours were drawn from realistic
observed distributions.

@@

We find that most of the confirmed lenses and candidates that are missed
by \sw are systems from the \rf sample, with fainter arcs and smaller $R_{\rm E}$.
The main reason why \rf found such candidates
is because it involves subtracting the light from the lens galaxy,
making it easier to detect the lensed images during both the automated
object-finding, and the visual inspection and classification
phases. This approach naturally improves the detection
efficiency at smaller $R_{\rm E}$ and for fainter systems. The \sw
volunteers were not shown any galaxy$-$subtracted images. Showing
galaxy$-$subtracted images might be a better strategy to adopt for future
lens searches at galaxy-scales with \sw. In
\Sref{sec:fn} below, we further explore and discuss why some of the confirmed
lenses were missed by \sw.

@@

Indeed, we have found 59 new medium-high grade
lens candidates that were not known
before. In \Fref{fig:isd}, we show the image separation distribution for
the known \rf and \af sample (green), for the \sw identified (known and
new) lens sample (blue) only and the combined \cfhtls sample of \rf, \af and
the new \sw lens sample (magenta). It is interesting to note that both
the \rf$+$\af and \sw samples have very similar profiles and thus, the profile of the
combined sample has not changed significantly. This implies that previous
constraints on the image separation distribution are robust and the \af
selected sample does not suffer from significant incompleteness for
medium to large $R_{\rm E}$. This is the regime that probes density
profiles of galaxy groups to clusters.

In the figure, we also show for comparison the theoretical predictions
corresponding to three density profiles, namely, isothermal sphere (IS),
NFW and a ``Total'' profile which has NFW and Hernquist
profiles combined with an adiabatically contracting model for the dark
matter component \citep{Gnedin2004}. These curves are taken from
\citet{More2012}, which gives details of the calculation of these
predictions.  With the updated sample of lens candidates, we confirm our
previous prediction that the mass density profiles of galaxy groups is
indeed consistent with the ``Total'' profile.

@@

Since in this project \sw enabled a visual search based on simple colour
composite images drawn directly from the survey,
it was difficult to detect many lens
candidates with a small $R_{\rm E}$ in the presence of a bright lensing
galaxy. In contrast, the \rf sample was
generated by working with lensing galaxy$-$subtracted images and this
led to increased detections of small image separation candidates. The
\sw interface did not show any galaxy subtracted images and hence,
this results in a quantitative difference between the \sw and the \rf
sample as a function of $R_{\rm E}$.

The \af is capable of finding some small image
separation lenses, but a lower limit at $R_{\rm E}=2\arcsec$ was imposed
by the \af team to simplify the selection function of their sample.
Thus, we can compare the \sw and \af samples at about $R_{\rm
E}>2\arcsec$. There is a good overlap between the two samples given that
most of these are candidates and could turn out not to be lenses. We again
caution the readers that the uncertainties on the measurements are not
quantified and may change the results to some extent.

@@

Lastly, in \Fref{fig:stackremg}, we show the relative distribution of
number of candidates from each sample as a function of the Einstein
radius and arc magnitude. The light blue colour shows the overlap between
the \sw and the \rf samples and the purple colour shows the overlap
between the \sw candidates and the \af samples. As noted earlier, the
\rf dominates the small $R_{\rm E} (<2\arcsec)$ detections although \sw does
find a modest number of candidates in this range. At larger $R_{\rm E}$,
\sw sample begins to dominate and is comparable to the \af sample.  As a
function of the arc magnitudes, all three samples have detections at all
magnitudes and median magnitudes for all samples is around $g\sim24.5$.
Relatively, the \rf sample spans a narrower range compared to the \sw
and \af sample. However, this can be verified only after understanding
and accounting for the systematic uncertainties in our measurements.

@@

\subsubsection{Blind lens search}

@@

The bottom panels of \Fref{fig:detmis}, show the trajectories of missed
lenses for visually easier and more difficult examples in red and green,
respectively.  In spite of some mild qualitative differences, both set
of trajectories have very similar behaviour. The trajectories in panel
(e) are typical of this sample in terms of Nclass and the dominance of
small negative kicks. Panel (f) represents a small fraction of this
sample where the kicks are only small and negative. The panel (g) shows
how some lenses receive a bunch of large positive kicks which are led to
rejection by still mostly small negative kicks. Finally, panel (h) shows
those cases of lenses which received almost sufficient number of large
positive kicks to be detected but ended up being rejected.

@@

Some of the key inferences are as follows.  i) The ratio of  large
positive kicks to small positive kicks for the detected sample is higher
than in the missed sample, suggesting that the fraction of high power
volunteers is large for the detected sample.  ii) The number of
classifications received by the missed sample is dominated by small
negative kicks. In contrast, for the detected sample there are
comparable contributions from all three types -- small positive kicks,
large positive kicks, and small negative kicks.  iii) The number of
classifications providing large negative kicks is lower for both the
detected and the missed samples. This is consistent with our expectation
that high power volunteers should not be making incorrect
classifications.  We conclude that one of the major factors in the \SW
system missing the known lenses is a lack of high power classifications.

@@

Changing the rejection and acceptance thresholds will likely increase
the rate of false positives along with improved completeness.  This will
need to be further quantified before detailed recommendations can be
made. However, dynamically assigning certain subjects to volunteers
according to various measures of their skill seems like a fruitful line
of investigation when seeking to improve the system performance in
future.

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.6]{det_mis_traj.pdf}
\includegraphics[scale=0.6]{det_mis_hist.pdf}
\caption{ \label{fig:detmis}
Left: Examples of \StageOne trajectories of some known lenses.
Upper panels show detected
lenses, lower panels show missed lenses (false negatives). Right:
Histogram of classification power received by known lenses.
Among the sample of missed
lenses, most classifications are from the low power volunteers
identifying these images incorrectly (i.e. $-\Delta$~log(P)) which
overshadows the small number of correct identifications (i.e.
$\Delta$~log(P)) coming from both the less and the high power volunteers
combined. For the detected lens sample, most classifications are correct
identifications coming from both low and high power volunteers.
}
\end{center}
\end{figure*}

@@

The discovery of many new lens candidates through the first \sw lens
search has demonstrated that the citizen scientists have successfully
taught themselves to identify lenses within a short span of time.  They
have found lens candidates which the algorithms failed to discover.
Upcoming and planned wide-field imaging surveys such as the DES, HSC and
LSST will produce formidable amounts of data.  Blind lens searches as
described here will be impractical with these very large surveys. However,
it should be possible to conduct a blind search on a sub-area of a large survey in
order to assess the performance of either the algorithms or the
volunteers, the results of which can be extrapolated to the entire survey.  As
demonstrated in this paper, any one approach for finding lenses from the
entire survey data may not be sufficiently complete and pure. Thus, combining
robotic methods for pre-selection with the citizen science approach for
visual screening might be a good strategy for finding lenses in these
large imaging surveys.

@@

%\begin{sideways}
%\begin{tabular}{llrrrrrrlrr}

@@

%\end{tabular}
%\end{sideways}

>>>>

\begin{abstract}
We report the discovery of 29 promising (and 59 total) new lens
candidates from the CFHT Legacy Survey (\cfhtls) based on about 11
million classifications performed by citizen scientists as part of the
first \sw lens search.  The goal of the blind lens search was to
identify lens candidates missed by robots (the \rf on galaxy scales and
\af on group/cluster scales) which had been previously used to mine the
\cfhtls for lenses.  We compare some properties of the samples detected
by these algorithms to the \sw sample and find them to be broadly
similar.  The image separation distribution calculated from the \sw
sample shows that previous constraints on the average density profile of
lens galaxies are robust. \sw recovers about 65\% of known lenses, while
the new candidates show a richer variety compared to those found by the
two robots. This detection rate could be increased to 80\% by only using
classifications performed by expert volunteers (albeit at the cost of a
lower purity), indicating that the training and
performance calibration of the citizen scientists is very important for
the success of \sw. In this work we present the SIMCT pipeline, used for
generating {\it in situ} a sample of realistic  simulated lensed images.
This training sample, along with the false positives identified during
the search, has a legacy value for testing future lens finding
algorithms. We make the pipeline and the training set publicly
available.
\end{abstract}

@@

\section{Training sample}
\label{sec:ts}

The simulated lenses are important to train citizen scientists who may be
new to the task of finding lenses, but they are also crucial for
analysing the classifications performed by the citizen scientists (more
details can be found in \PaperOne, but see \Sref{sec:swap} below for a brief
summary). In this section, we describe the framework used for generating the
simulated lens sample, give details of the sample itself along with
some of its known limitations and also describe the sample of duds and
impostors.

@@

\subsection{Methodology to simulate lenses}
\label{sec:simmethod}

@@

We also add external shear at the centre of the potential lensing galaxy
drawn randomly from a set range (see \Tref{tab:thresh}. The shear is
expected to affect the lens cross-section for a small number of cases
when the shear strength is high in addition to high lens ellipticity or
the PA of the shear is almost orthogonal to that of the lens
ellipticity. However, the effect of shear on the lens cross-section is
expected to be small for most of the cases and is ignored in the current
implementation of SIMCT.

@@

Once all the parameters are determined for the lens and source models,
we once again use \gravlens to generate simulated lensed images.  After
accounting for the shot noise in the lensed images and convolving them
with the seeing in each of the filters, the simulated image is added to
the real \cfhtls~image centred on the galaxy chosen to act as a
lens. Note that we ensure that the lensed galaxies and lensed quasars
are not superposed on the same ``lensing'' galaxy.  Similarly,
these ``lensing'' galaxies at the galaxy scales are ensured to be
distinct from those chosen for the group scales. The framework for the
group-scale is described below.

\begin{figure}
\begin{center}
\includegraphics[scale=1.2]{distrib_remu.pdf}
\caption{ \label{fig:remudist}
Einstein radius and total magnification distributions for all types of lenses. The solid (blue)
curves show the theoretical prediction assuming an SIS model at galaxy-scales
and a total (NFW+Hernquist) model at group scales taken from \citep{More2012}.
}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=1.3]{lensprop.pdf}
\caption{ \label{fig:lensprop}
Distributions of properties of the ``lensing'' galaxies of the simulated
sample compared to the known lens sample SARCS.
}
\end{center}
\end{figure*}

@@

Next, we consider the redshift, magnitude and ellipticity distributions
of the ``lensing'' galaxies from the simulated sample as shown in \Fref{fig:lensprop}. For reference,
we also show SARCS lenses from \citet{More2012}, with arbitrary
normalizations. We find that the properties of the foreground lenses in
the simulated and the real lens samples are broadly similar.

We produce catalogs with lens and source properties for each of the
three types of simulated lenses.  The catalogs typically have lens position,
redshift, magnitudes, Einstein radius, ellipticity (whenever available)
and shear (for galaxy-scale lenses only). For the background sources, we
provide the offset from the lens centre, redshift, magnitudes, total
magnification, number of lensed images. Additionally, when possible,
ellipticity and effective radius of the background galaxies have also
been provided. These catalogs are available from
\texttt{https://github.com/anupreeta27/SIMCT} and the
simulated lens image sample is available from the authors on request.

@@

The parameters required by the models' various scaling relations
primarily depend on the photometry of the galaxies, groups and quasars
detected in the survey. For galaxy-scale lenses, the fainter or higher redshift
galaxies, chosen to act as lenses, tend to have poor photometric redshift
measurements. Consequently these galaxies were occasionally assigned the wrong
luminosity and velocity dispersion estimates, resulting in
simulated lenses which look implausible or unrealistic.  For example,
the lensed images for some of the failed simulations have larger image
separation than what one would expect from the luminosity and/or size of the
galaxy. We roughly expect mass to follow light, so more massive galaxies
typically look brighter and/or bigger.

@@

\subsection{Duds and Impostors}
\label{sec:dfp}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.6]{cand_fp_P_frac.pdf}
\caption{ \label{fig:stackP}
Distribution of different types of candidates as a function of the
posterior probability $P$, obtained at the end of \StageTwo. The types of the candidates are the false
positives (FPs), the new candidates and the known candidates. The new
and known candidates have higher detection rate for higher values of $P$,
as expected.}
\end{center}
\end{figure}

@@

Each subject (image cutout) is assigned a prior probability of
$2\times10^{-4}$ of containing a lens system. Every volunteer
is assigned an agent characterised by a $2\times2$ confusion matrix~$\CM$,
which quantifies the volunteer's ability to correctly classify an image
as containing a lens ($\PL = P_L$) or not containing a lens ($\PD = P_D$).
The values of
these confusion matrix elements are determined based on the performance of the
volunteer on the training sample, specifically, $P_L$ (and $P_D$) is
determined based on the fraction of simulated lenses (and, respectively, duds)
correctly classified. After every classification, the agent updates the
probability of the classified subject based on the volunteer's classification
and the confusion matrix, according to Bayes' theorem.
The agent's confusion matrix is updated after the
classification of every training image. The thresholds for the
probabilities to accept or reject a subject if it contains a lens or does
not contain one can be chosen in SWAP. In \StageOne, those images which cross
these threshold values are ``retired'', and are not subsequently shown to the
volunteers. In this way, the crowd can use its time efficiently in
inspecting previously unclassified subjects.

SWAP was run nightly during \StageOne in order to retire subjects and inject new
ones in to the classification stream. The subjects that passed the detection
threshold at the end of \StageOne were served again at \StageTwo for careful
re-inspection. The goal of \StageOne inspection was to maximise completeness
and that of \StageTwo was to maximise purity. Each subject, after \StageTwo, has a final posterior
probability $P$. In the ideal case, all images containing lenses will have high $P$
values and those without lenses will have low $P$ values. In practice, we expect a
small fraction of the real lenses (or non-lenses) to be assigned low (or high) $P$
values, thereby decreasing the completeness (or purity) of the final lens
sample. As this is the first lens search with \sw, we want to find a
threshold $P$ value which will result in acceptable levels of completeness and
purity of the final sample of lens candidates.

To achieve this, we selected a total of 665 subjects with $P>0.3$
at \StageTwo which were then visually inspected by three of us (as ``lens experts'',
 AM, AV, PJM).  Each images was assigned a grade on a scale of 0 to 3,
representing those images
0) unlikely to contain a lens, 1) possibly containing a lens, 2) probably
containing a lens and 3) almost certainly containing a
lens. The final sample of \sw-\cfhtls lens candidates was
then produced by selecting candidates above a threshold on the
averaged grade~$G$, as described in the next section.

@@

The new \sw lens sample presented here illustrates some of
the advantages of having
citizen scientists find lenses through visual inspection. An algorithm,
by definition will find objects that adhere to a selection criteria that
uses either geometry or flux information from an image. On the other
hand, citizen scientists can interpolate over or
extrapolate beyond the basic selection criteria provided to them.  For
example, the lower blue arc in SW7 is split by a small red galaxy.  An
algorithm typically fails to detect such arcs because the arc is broken
into smaller arclets which then falls below the minimum length or area
allowed for an arc to be detected. Human inspectors have no
problem in interpolating over the broken blue arc over the red galaxy,
understanding that it is a single long arc. The system SW20 has
point-like lensed images which cannot be detected by arc finding
algorithm, whereas the ring finding algorithm may have missed this because of
the atypical colour and structure of the lensing galaxy. Detection of red arcs, for
example, as seen in the SW39 candidate, shows how the volunteers
extrapolate on the colour parameter: the training sample contains
predominantly blue arcs, because the source colours were drawn from realistic
observed distributions.

@@

We find that most of the confirmed lenses and candidates that are missed
by \sw are systems from the \rf sample, with fainter arcs and smaller
$R_{\rm E}$.  The main reason why \rf found such candidates is because
it involves subtracting the light from the lens galaxy, making it easier
to detect the lensed images during both the automated object-finding,
and the visual inspection and classification phases. This approach
naturally improves the detection efficiency at smaller $R_{\rm E}$ and
for fainter systems. The \sw volunteers were not shown any
galaxy$-$subtracted images. Showing galaxy$-$subtracted images might be
a better strategy to adopt for future lens searches at galaxy-scales
with \sw. However, we note that accurate modelling and subtraction
of the galaxy light profile in different bands is challenging and better
techniques are being actively developed to enhance detections of lenses
at small image separations. In \Sref{sec:fn} below, we further explore
and discuss why some of the confirmed lenses were missed by \sw.

@@

Indeed, we have found 59 new medium-high grade lens candidates that were
not known before. In \Fref{fig:isd}, we show the image separation
distribution using all the known and new lens candidates. The different
data points are  the known \rf and \af sample (green), the \sw
identified (known and new) lens sample (blue) only and the combined
\cfhtls sample of \rf, \af and the new \sw lens sample (magenta). It is
interesting to note that both the \rf$+$\af and \sw samples have very
similar profiles and thus, the profile of the combined sample has not
changed significantly. This implies that previous constraints on the
image separation distribution are robust and the \af selected sample
does not suffer from significant incompleteness for medium to large
$R_{\rm E}$. This is the regime that probes density profiles of galaxy
groups to clusters.

In the figure, we also show for comparison the theoretical predictions
corresponding to three density profiles, namely, isothermal sphere (IS),
NFW and a ``Total'' profile which has NFW and Hernquist profiles
combined with an adiabatically contracting model for the dark matter
component \citep{Gnedin2004}. These curves are taken from
\citet{More2012}, which gives details of the calculation of these
predictions.  With the updated sample of lens candidates, we confirm our
previous prediction that the mass density profiles of galaxy groups is
indeed consistent with the ``Total'' profile.  At smaller image
separations ($\lesssim 2$~arcsec), the ``Total'' profile converges to
isothermal like case and assuming these predictions are reliable, we
find that the lens samples have very low completeness. This is not too
surprising compared to the 40\% completeness expected for the \rf sample
\citep{Gavazzi2014}.

@@

%Since in this project \sw enabled a visual search based on simple colour
%composite images drawn directly from the survey,
%it was difficult to detect many lens
%candidates with a small $R_{\rm E}$ in the presence of a bright lensing
%galaxy. In contrast, the \rf sample was
%generated by working with lensing galaxy$-$subtracted images and this
%led to increased detections of small image separation candidates. The
%\sw interface did not show any galaxy subtracted images and hence,
%this results in a quantitative difference between the \sw and the \rf
%sample as a function of $R_{\rm E}$.
%
%The \af is capable of finding some small image
%separation lenses, but a lower limit at $R_{\rm E}=2\arcsec$ was imposed
%by the \af team to simplify the selection function of their sample.
%Thus, we can compare the \sw and \af samples at about $R_{\rm
%E}>2\arcsec$. There is a good overlap between the two samples given that
%most of these are candidates and could turn out not to be lenses. We again
%caution the readers that the uncertainties on the measurements are not
%quantified and may change the results to some extent.
%

@@

In \Fref{fig:stackremg}, we show the relative distribution of
number of candidates from each sample as a function of the Einstein
radius and arc magnitude. The light blue colour shows the overlap between
the \sw and the \rf samples and the purple colour shows the overlap
between the \sw candidates and the \af samples. As noted earlier, the
\rf dominates the small $R_{\rm E} (<2\arcsec)$ detections although \sw does
find a modest number of candidates in this range. At larger $R_{\rm E}$,
\sw sample begins to dominate and is comparable to the \af sample.  As a
function of the arc magnitudes, all three samples have detections at all
magnitudes and median magnitudes for all samples is around $g\sim24.5$.
Relatively, the \rf sample spans a narrower range compared to the \sw
and \af sample. However, this can be verified only after understanding
and accounting for the systematic uncertainties in our measurements.

@@

\subsubsection{Lens positions within the image cutouts}

@@

The bottom panels of \Fref{fig:detmis}, show the trajectories of missed
lenses for the cases which are visually easier (red) and more
difficult (green) to identify.  In spite of some mild
qualitative differences, both set of trajectories have very similar
behaviour. The trajectories in panel (e) are typical of this sample in
terms of Nclass and the dominance of small negative kicks. Panel (f)
represents a small fraction of this sample where the kicks are only
small and negative. The panel (g) shows how some lenses receive a bunch
of large positive kicks which are led to rejection by still mostly small
negative kicks. Finally, panel (h) shows those cases of lenses which
received almost sufficient number of large positive kicks to be detected
but ended up being rejected.

@@

Some of the key inferences are as follows. i) The ratio of positive
kicks to negative kicks for the detected sample is higher than in the
missed sample, suggesting that the fraction of volunteers making
positive kicks is higher for the detected sample. ii) The number of
classifications received by the missed sample is dominated by small
negative kicks. In contrast, for the detected sample there are
comparable contributions from all three types -- small positive kicks,
large positive kicks, and small negative kicks.  iii) The number of
classifications providing large negative kicks is lower for both the
detected and the missed samples. This is consistent with our expectation
that high power volunteers should not be making incorrect
classifications.  We conclude that one of the major factors in the \SW
system missing the known lenses is a lack of high power classifications.

@@

Changing the rejection and acceptance thresholds will likely 
decrease the purity along with improved completeness. This will
need to be further quantified before detailed recommendations can be
made. However, dynamically assigning certain subjects to volunteers
according to various measures of their skill seems like a fruitful line
of investigation when seeking to improve the system performance in
future.

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.6]{det_mis_traj.pdf}
\includegraphics[scale=0.6]{det_mis_hist.pdf}
\caption{ \label{fig:detmis}
Left: Examples of \StageOne trajectories of some known lenses.  Upper
panels show detected lenses, lower panels show missed lenses (false
negatives). The green trajectories for the detected sample are
counterparts of the red and green trajectories of the missed sample
except that the kicks are positive for the detected sample. The red
trajectories of the detected sample demonstrate that sufficient number
of positive large kicks can lead to the detection of the lenses. Within the
missed sample, the red and green correspond to visually easier and more
difficult to identify systems, respectively. Right: Histogram of classification
power received by known lenses.  Among the sample of missed lenses, most
classifications are from the low power volunteers identifying these
images incorrectly (i.e.  $-\Delta$~log(P)) which overshadows the small
number of correct identifications (i.e.  $\Delta$~log(P)) coming from
both the less and the high power volunteers combined. For the detected
lens sample, most classifications are correct identifications coming
from both low and high power volunteers. }
\end{center}
\end{figure*}

@@

The discovery of many new lens candidates through the first \sw lens
search has demonstrated that the citizen scientists have successfully
taught themselves to identify lenses within a short span of time.  They
have found lens candidates which the algorithms failed to discover.
Upcoming and planned wide-field imaging surveys such as the DES, HSC,
Euclid and LSST will produce formidable amounts of data. Blind lens searches as
described here will be impractical with these very large surveys. However,
it should be possible to conduct a blind search on a sub-area of a large survey in
order to assess the performance of either the algorithms or the
volunteers, the results of which can be extrapolated to the entire survey.  As
demonstrated in this paper, any one approach for finding lenses from the
entire survey data may not be sufficiently complete and pure. Thus, combining
robotic methods for pre-selection with the citizen science approach for
visual screening might be a good strategy for finding lenses in these
large imaging surveys.

@@

@@
